\onehalfspacing
\chapter*{Acknowledgements}
	This work reflects the endless days I have spent learning, researching, and growing throughout the past several years and would not have been possible without the gracious assistance of the considerable number of people supporting me.

	My supervisor, Dr. Walied Moussa has been a constant source of inspiration and learning for me. His enthusiam and tenacity for research became a model for this work early on in the process. I would like to thank him for providing me with this alongside all the resources and support I needed to complete this work.

	I would also like to thank my co-supervisor, Dr. Martin Ferguson-Pell for believing in me since I was an undergrad and continually providing me with opportunities to advance my learning. Despite his tremendous responsibilities, he always made time for me when I needed it and has always provided valuable input and guidance.

	I am incredibly grateful for the wonderful guidance, support, and supervision of the entire Project SMART Pressure Ulcer group along with the rest of the PIs and trainees of the Project SMART team. Their gentle leadership, kind friendship, and impressive ability continually inspired me to pursue my best and live up to their remarkable example.

	Lastly, I would like to thank my family and friends who have kept faith with me and my work since its inception while only marginally mocking me about my career choices.

	I truly stand as a dwarf upon the shoulders of giants.